Tampering Detection In Low-Power Smart Cameras

### 2015-05-19 paper.tex
inserite note Claudio

\author{Adriano Gaibotti\inst{1} \and Claudio Marchisio\inst{1} \and Alexandro Sentinelli\inst{1} \and Giacomo Boracchi\inst{2}}

\institute{ 
	STMicroelectronics, Advanced System Technology, Via Camillo Olivetti 2, 20864, Agrate Brianza (MB), Italy\\
	\email{\{adriano.gaibotti, claudio.marchisio, alexandro.sentinelli\}@st.com}
	\and
	Politecnico di Milano, Dipartimento di Elettronica, Informazione e Bioingegneria (DEIB), Via Ponzio 34/5, 20133, Milano (MI), Italy\\
	\email{giacomo.boracchi@polimi.it}
}
\maketitle

@@

\section{Introduction}\label{sec:introduction}
%\gi{Adriano: decidi che email tenere, non tutte e due :)}

@@

% What is the problem?
When cameras operate outdoor and in harsh environments, dust, rain drops or snow flakes might lie on the camera lens resulting in blurry pictures, as in Fig. \ref{fig:pioggia}, or in partial occlusions of the scene, as in Fig. \ref{fig:neve}. Similarly, other intentional attacks like displacing the camera, changing its focus, or spraying some opaque or glossy liquid over the lenses, would result in heavily compromised pictures, that would be surely useless for monitoring purposes. We refer to these events/attacks as tampering. In some cases, tampering is easy to detect, e.g., when the camera integrity is affected and the device goes out-of-order. However, in many other situations, namely when the device is not physically damaged but the correct interpretation of the scene or of small important details is prevented (e.g., the identification of licence plates), tampering detection is not straightforward and requires image-analysis algorithms.

@@

\gi{Qui ST pu\'o aggiungere qualche esempio di applicazione qui o menzionare dispositivi di riferimento (con tanto di link a datasheet). Magari aggiungendo che le batterie recenti permettono operativit\'a di due anni a questi regimi.}
We here consider low-power cameras, which are battery powered and that have to operate at very low frame-rates (e.g. one frame every minute or more) and which have a constrained computational power or memory availability. As an example, consider wireless multimedia sensor networks (WMSN) \cite{akyildiz2007survey} where nodes are wirelessy connected smart-cameras, that can acquire and transmit images at regular time interval or upon requests. In these WMSN, notes are often not connected to the power supply and have to operate battery-powered, possibly implementing energy harvesting mechanisms \gi{REFERENCES, magari riprescando quelle del paper di TIM}. Even though these devices are not employed in critical surveillance applications, low-power smart cameras are becoming popular in distributed monitoring of wide environments due to their low price \gi{possiamo mettere qualche REFERENCE}. Tampering detection is very important in low-power smart cameras, also considering that tampered frames should not be transmitted over the network, saving energy-demanding operations like the activation of the radio module.

% Why is it hard? (E.g., why do naive approaches fail?)
Tampering detection in low-power smart cameras is much more challenging than in conventional surveillance cameras. Beside computational aspects -- such as the number of operations per pixels allowed and the memory availability -- the big issue is that low-power smart cameras typically operate at very low-frame rates (e.g., less than one frame per minute), and the acquired sequence does not evolve smoothly. This prevents the use of learned background models and the analysis of foreground variations \gi{REFERENCE su BKGR SUBTRACTION}. When dynamic environments are acquired at low frame rates, like the example depicted in Fig. \ref{fig:buenosAires}, two consecutive frames might be very different because of changes in the scene and in the light conditions: smart cameras have to correctly distinguish between these \emph{normal} changes and changes due to camera displacement or blur/defocus. Moreover, il low-power smart cameras, tampering has to be reliably detected because false alerts would lead to unnecessary data-transmissions thus increasing the energy consumption.

@@

%What are the key components of my approach and results? Also include any specific limitations.
We here propose an algorithm to detect both camera defocus and of displacement, as stated in Section \ref{sec:probForm}. The algorithm relies on simple indicators that are computed with a low computational complexity (Section \ref{subsec:Indicators}) and leverages an outlier detection technique to detect frames yielding anomalous indicators as related to a tampering event (Section \ref{subsec:MonitoringScheme}). In particular, we perform a preliminarily partitioning of the scene into nonoverlapping regions, and separately compute and monitor indicators over different regions. Scene partitioning is defined by clustering feature vectors gathering the indicators in different pixels, thus performing a very coarse segmentation of the image (Section \ref{subsec:Segmentation}). Regions are computed during the initial configuration of the algorithm and as such do not implies any computational overhead w.r.t. operating on the whole image. Our experiments in Section \ref{sec:experiments} show that regions substantially improve the detection of camera displacements,  while when monitoring indicators meant to detect blur/defocus, it is more convenient to analyze the whole scene. Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

\begin{figure}[t!]
\centering
\subfigure[]{\label{fig:pioggia} \includegraphics[width=0.4\linewidth]{Immagini/pioggia}}
\subfigure[]{\label{fig:neve} \includegraphics[width=0.4\linewidth]{Immagini/neve}}
\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
\label{fig:tampering}
\end{figure}

@@

\begin{algorithm}[tp]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Input}: $\gamma$, $T_{o}$, $\{R_k\}, k=1,\dots,K$ \\
	\textbf{Configuration}:\\
%	\lnl{DISPL-Tr1} Extract regions $\{\mathcal{R}_k\}, k=1,\dots,K$  \\
	\lnl{DISPL-Tr2} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DISPL-Tr3} Get frame $z_t$ \\
		\lnl{DISPL-Tr4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Tr5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
		}
	}
	\lnl{DISPL-Tr6} \For{$k=1,\dots,K$}{
		\lnl{DISPL-Tr7} Compute $\sigma_l^k$\\
	}
	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$ \\
		\lnl{DISPL-Test3} $n_l = 0$ \\
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
			\lnl{DISPL-Test6} \If{$\partial l^k(t) < -\gamma \sigma_l^k \vee \partial l^k(t) > \gamma \sigma_l^k $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} $z_t$ is a tampered frame\\
		}
	}   
	\caption{Tampering detection algorithm}
	\label{alg:DISPL}
\end{algorithm}
%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

\section{Experiments}\label{sec:experiments}
The proposed algorithm has been implemented in MATLAB, and has been tested on two datasets.
The first one refers to frame sequences taken from webcams recording some parts of cities (as frames illustrated in Figure \ref{fig:buenosAires}), where we have introduced some synthetically generated tampering events:
defocus has been simulated using gaussian filters, while displacement has been created with concatenation of similar frame sequences.
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{Immagini/buenosAires}
	\caption{Example of frame sequence taken from webcam. Frames have been acquired every $30$ seconds.}
	\label{fig:buenosAires}
\end{figure}
\begin{figure}
\centering
\subfigure[]{\label{fig:buenosAiresDef} \includegraphics[width=1\linewidth]{Immagini/buenosAiresDef}}
\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=1\linewidth]{Immagini/buenosAiresDispl}}
\caption{Examples of synthetically generated tampering events. \textbf{(a)} Defocus generated with gaussian filters on frames \textit{d} and \textit{e}. \textbf{(b)} Displacement created doing concatenation of similar sequences on frames \textit{d} and \textit{e}.}
\label{fig:buenosAiresTamp}
\end{figure}
In some cases these sequences contained real tampering events, as in Figure \ref{fig:fulvioTestiDispl}.\\
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/fulvioTestiDispl}
\caption{Example of sequence taken from webcam in which there is a real displacement (frame \textit{d})}
\label{fig:fulvioTestiDispl}
\end{figure}
The second dataset was taken using a Raspberry Pi Model B+, with its camera module, and the tampering was introduced by moving the device or putting water on the camera.\\
Four figures of merit have been suggested to assess the performance of the proposed algorithm:\\
\begin{description}
	\item[TP]  True positives. It measures the number of tampering events correctly detected by the algorithm.\\ 
	\item[TN]  True negatives. It measures the number of frames without tampering that are not detected by the algorithm. \\ 
	\item[FP]  False positives. It measures the number of tampering events erroneously detected by the algorithm.\\ 
	\item[FN]  False negatives. It measures the number of tampering events not detected by the algorithm. \\ 
\end{description} 
These indicators are computed varying the parameter $\gamma$, which defines the thresholds for the one-shot monitoring. 
This permits us to generate \textit{ROC curves}, where on the x-axis there is:
\[1-\text{SPECIFICITY}_\gamma = 1-\frac{\text{TN}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}=\frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma},\]
while on th y-axis there is:
\[\text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}.\]
The construction of these curves permits us to

>>>>

\author{Adriano Gaibotti\inst{1}\inst{2} \and Claudio Marchisio\inst{2} \and Alexandro Sentinelli\inst{2} \and Giacomo Boracchi\inst{1}}

\institute{ 
	Politecnico di Milano, Dipartimento di Elettronica, Informazione e Bioingegneria (DEIB), Via Ponzio 34/5, 20133, Milano (MI), Italy\\
	\email{adriano.gaibotti@mail.polimi.it, giacomo.boracchi@polimi.it}
	\and
	STMicroelectronics, Advanced System Technology, Via Camillo Olivetti 2, 20864, Agrate Brianza (MB), Italy\\
	\email{\{adriano.gaibotti, claudio.marchisio, alexandro.sentinelli\}@st.com}
}
\maketitle

@@

\section{Introduction}\label{sec:introduction}
\gi{Adriano: decidi che email tenere, non tutte e due :)}

@@

% What is the problem?
When cameras operate outdoor and in harsh environments, dust, rain drops or snow flakes might lie on the camera lens resulting in blurry pictures, as in Fig. \ref{fig:pioggia}, or in partial occlusions of the scene, as in Fig. \ref{fig:neve}. Similarly, other intentional attacks like displacing the camera, changing its focus, or spraying some opaque or glossy liquid over the lenses, would result in heavily compromised pictures, that would be surely useless for monitoring purposes. We refer to these events/attacks as tampering. In some cases, tampering is easy to detect, e.g., when the camera integrity is affected and the device goes out-of-order. However, in many other situations, namely when the device is not physically damaged,	 but the correct interpretation of the scene or of small important details is prevented (e.g., the identification of licence plates), tampering detection is not straightforward and requires image-analysis algorithms.

@@

\gi{Qui ST pu\'o aggiungere qualche esempio di applicazione qui o menzionare dispositivi di riferimento (con tanto di link a datasheet). Magari aggiungendo che le batterie recenti permettono operativit\'a di due anni a questi regimi.}\cl{Verifico cosa possiamo dire del SecSoc.}
This work expressly targets low-power and ultra-low-power smart cameras. Such devices typically operate at very low frame-rates (e.g. possibly less than one frame every minute), with constrained computational power and memory, and are battery powered (typically lasting one or two years). 
% We here consider low-power cameras, which are battery powered and that have to operate at very low frame-rates (e.g. one frame every minute or more) and which have a constrained computational power or memory availability.
As an example, consider Wireless Multimedia Sensor Networks (WMSN) \cite{akyildiz2007survey} where nodes are wirelessy connected smart-cameras, that can acquire and transmit images at regular time interval or upon requests. Often, in WMSN, the units are not connected to the power supply and have to operate with batteries, possibly implementing energy harvesting mechanisms \gi{REFERENCES, magari riprescando quelle del paper di TIM}. Even though these devices are not employed in critical surveillance applications, low-power smart cameras are becoming popular in distributed monitoring of wide environments due to their low cost and maintenance requirements \gi{possiamo mettere qualche REFERENCE}. Tampering detection is thus very important in low-power smart cameras, also considering that tampered frames should be identified to avoid unnecessary energy-demanding operations like the local processing or radio activation for transmission over the network.

% Why is it hard? (E.g., why do naive approaches fail?)
Tampering detection in low-power smart cameras is much more challenging than in conventional surveillance cameras. Beside computational aspects -- such as the number of operations per pixels allowed -- the big issue is that low-power smart cameras typically operate at very low-frame rates (e.g., less than one frame per minute), and the acquired sequence does not evolve smoothly. This prevents the use of learned background models and the analysis of foreground variations \gi{REFERENCE su BKGR SUBTRACTION}. When dynamic environments are acquired at low frame rates, like the example depicted in Fig. \ref{fig:buenosAires}, two consecutive frames might be very different because of changes in the scene and in the light conditions: smart cameras have to correctly distinguish between these \emph{normal} changes and changes due to camera displacement or blur/defocus. Moreover, in low-power smart cameras, tampering has to be reliably detected because false alerts would lead to unnecessary energy waste.

@@

%What are the key components of my approach and results? Also include any specific limitations.
This work presents an algorithm to detect both camera defocus and of displacement, as stated in Section \ref{sec:probForm}. The algorithm relies on simple indicators that are computed with a low computational complexity (Section \ref{subsec:Indicators}) and leverages an outlier detection technique to detect frames yielding anomalous indicators as related to a tampering event (Section \ref{subsec:MonitoringScheme}). In particular, we perform a preliminarily partitioning of the scene into nonoverlapping regions, and separately compute and monitor indicators over different regions. Scene partitioning is defined by clustering feature vectors gathering the indicators in different pixels, thus performing a very coarse segmentation of the image (Section \ref{subsec:Segmentation}). Regions are computed during the initial configuration of the algorithm and as such do not implies any computational overhead w.r.t. operating on the whole image. Our experiments in Section \ref{sec:experiments} show that regions substantially improve the detection of camera displacements, while when monitoring indicators meant to detect blur/defocus, it is more convenient to consider the whole scene at once. Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

\begin{figure}[t!]
\centering
\subfigure[]{\label{fig:pioggia} \includegraphics[width=0.4\linewidth]{Immagini/pioggia}}
\subfigure[]{\label{fig:neve} \includegraphics[width=0.4\linewidth]{Immagini/neve}}
\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens, while in Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens.}
\label{fig:tampering}
\end{figure}

@@

\begin{algorithm}[tp]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Input}: $\gamma$, $T_{o}$, $\{\mathcal{R}_k\}, k=1,\dots,K$ \\
	\textbf{Configuration}:\\
%	\lnl{DISPL-Tr1} Extract regions $\{\mathcal{R}_k\}, k=1,\dots,K$  \\
	\lnl{DISPL-Tr2} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DISPL-Tr3} Get frame $z_t$ \\
		\lnl{DISPL-Tr4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Tr5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $\mathcal{R}_k$\\
		}
	}
	\lnl{DISPL-Tr6} \For{$k=1,\dots,K$}{
		\lnl{DISPL-Tr7} Compute $\sigma_l^k$\\
	}
	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$ \\
		\lnl{DISPL-Test3} $n_l = 0$ \\
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $\mathcal{R}_k$\\
			\lnl{DISPL-Test6} \If{$\partial l^k(t) < -\gamma \sigma_l^k \vee \partial l^k(t) > \gamma \sigma_l^k $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} $z_t$ is a tampered frame\\
		}
	}   
	\caption{Tampering detection algorithm}
	\label{alg:DISPL}
\end{algorithm}
\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

\section{Experiments}\label{sec:experiments}
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/buenosAires}
\caption{}
\label{fig:buenosAires}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/buenosAiresDef}
\caption{}
\label{fig:buenosAiresDef}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/fulvioTestiDispl}
\caption{}
\label{fig:fulvioTestiDispl}
\end{figure}

\subsection{Dataset Description}\label{subsec:Dataset}
\gi{Adriano: Prova a mettere qua le info}
The proposed method have been tested on a dataset of frame sequences in which there were tampering events.
A part of this dataset was taken using a Raspberry Pi with its camera module, and the tampering was introduced by moving the device or putting water on the camera.
The other part of this dataset is made of frame sequences taken from webcams available on the Internet. 
In these sequences there were a few events of displacements or defocus, but to have a larger set of tampering events we have simulated them.
In particular we have used gaussian filtering for simulating defocus events, and concatenation of similar sequences for simulating displacement events.\\
